---
title: "Results"
author: "Anton Kalén"
date: "12/29/2020"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup}

# Setup
knitr::opts_knit$set(root.dir = here::here())
knitr::opts_chunk$set(echo = FALSE)
options(mc.cores = 4L)


# Load packages
library(targets)
library(dplyr)
library(tidyr)
library(loo)
library(tidybayes)
library(bayesplot)

# Load targets
tar_load(senior_players)
tar_load(player_data)
tar_load(generation_data)
tar_load(country_data)
tar_load(nr_youth_mod)
tar_load(nr_youth_lic_players_mod)
tar_load(nr_youth_pred_draws)
tar_load(nr_youth_lic_players_draws)
tar_load(nr_youth_ranking_mod)
tar_load(nr_youth_ranking_lic_players_mod)
tar_load(nr_youth_senior_country_mod)
tar_load(nr_youth_senior_lic_players_country_mod)
tar_load(nr_youth_senior_generation_mod)
tar_load(nr_youth_senior_lic_players_generation_mod)
```

## Model diagnostics

```{r}
models <- tibble(
  model = c(
    list(nr_youth_mod), 
    list(nr_youth_lic_players_mod),
    list(nr_youth_ranking_mod),
    list(nr_youth_ranking_lic_players_mod),
    list(nr_youth_senior_country_mod),
    list(nr_youth_senior_lic_players_country_mod),
    list(nr_youth_senior_generation_mod),
    list(nr_youth_senior_lic_players_generation_mod)
  )
)

models_divergent <- models %>% 
  rowwise() %>% 
  transmute(
    divergent = sum(nuts_params(model, pars = "divergent__")$Value),
    rhat = max(rhat(model))
  )

models_divergent

```


## Descriptives

```{r}
country_data %>% 
  count(gender)
```

```{r}
generation_data %>% 
  count(gender)
```
```{r}
player_data %>% 
  count(gender)
```


```{r}
player_data %>% 
  filter(senior >= 0) %>% 
  count(gender)
```

## Senior debut age
```{r}
senior_players %>% 
  group_by(gender, played_youth) %>% 
  summarise(
    quant = c(.25,.5,.75),
    value = quantile(senior_debut_age, quant, na.rm = TRUE)
  )
```

## Selection strategy

Avg nr players per generation in countries:

```{r}
# Avg nr youth
country_data %>% 
  group_by(gender) %>% 
  summarise(
    nr_youth_mean = mean(nr_youth_m), 
    nr_youth_sd = sd(nr_youth_m),
    cv_youth_mean = mean(nr_youth_cv),
    cv_youth_sd = sd(nr_youth_cv)
  )
```

Highest and lowest means:

```{r}
country_data %>% 
  group_by(gender) %>% 
  filter(nr_youth_m == max(nr_youth_m) | nr_youth_m == min(nr_youth_m)) %>% 
  select(gender, country, nr_youth_m)
```

Diff in mean:

```{r}
nr_youth_pred_draws %>% 
  group_by(gender, country, .draw) %>% 
  summarise(.prediction = mean(.prediction)) %>% 
  group_by(gender, .draw) %>% 
  filter(.prediction == max(.prediction) | .prediction == min(.prediction)) %>% 
  mutate(country = if_else(.prediction == max(.prediction), "max", "min")) %>% 
  pivot_wider(id_cols = c(.draw), names_from = c(gender, country), values_from = .prediction) %>% 
  mutate(men = Men_max - Men_min, women = Women_max - Women_min) %>% 
  ungroup() %>% 
  mean_hdi(men, women)
```


Highest and lowest cv:

```{r}
country_data %>% 
  group_by(gender) %>% 
  filter(nr_youth_cv == max(nr_youth_cv) | nr_youth_cv == min(nr_youth_cv)) %>% 
  select(gender, country, nr_youth_cv)
```


Diff gender:

```{r}
country_pred <- nr_youth_pred_draws %>% 
  group_by(.draw, gender, country) %>% 
  summarise(country_mean = mean(.prediction), country_cv = 100 * sd(.prediction) / country_mean)


country_pred %>% 
  summarise(gender_mean = mean(country_mean), gender_cv = mean(country_cv)) %>% 
  pivot_wider(names_from = gender, values_from = c(gender_mean, gender_cv)) %>% 
  mutate(mean_diff = gender_mean_Men - gender_mean_Women, cv_diff = gender_cv_Men - gender_cv_Women) %>% 
  ungroup() %>% 
  mean_hdi(mean_diff, cv_diff)
```

Countries above or below average:

```{r}
country_prob_sup <- country_pred %>% 
  mutate(gender_mean = mean(country_mean), gender_cv = mean(country_cv)) %>% 
  group_by(gender, country) %>% 
  summarise(
    prob_sup_m = mean(country_mean > gender_mean), 
    prob_sup_cv = mean(country_cv > gender_cv)
  ) %>% 
    mutate(
    group_m = dplyr::case_when(
        prob_sup_m > .95 ~ "Above",
        prob_sup_m < (1 - .95) ~ "Below",
        TRUE ~ "Average"
      ),
    group_cv = dplyr::case_when(
        prob_sup_cv > .95 ~ "Above",
        prob_sup_cv < (1 - .95) ~ "Below",
        TRUE ~ "Average"
      )
  )

country_prob_sup %>% 
  count(group_m)
```
Countries above or below average:

```{r}
country_prob_sup %>% 
  count(group_cv)
```

```{r}
country_prob_sup %>% 
  filter(group_cv %in% c("Above", "Below"))
```

### Licenced players moderator

Descriptive stats nr licenced players:

```{r}
country_data %>% 
  group_by(gender) %>% 
  summarise(
    quant = c(.25,.5,.75),
    value = quantile(as.integer(players_lic), quant, na.rm = TRUE)
  )
```

Min-max:

```{r}
country_data %>% 
  drop_na(players_lic) %>% 
  group_by(gender) %>% 
  filter(players_lic == max(players_lic) | players_lic == min(players_lic)) %>% 
  select(gender, country, players_lic)
```


Model comparison:

```{r}
nr_youth_loo <- loo(nr_youth_mod)
nr_youth_lic_players_loo <- loo(nr_youth_lic_players_mod)
print(loo_compare(nr_youth_loo, nr_youth_lic_players_loo), simplify = FALSE)
```


Diff gender:

```{r}
country_lic_players_pred <- nr_youth_lic_players_draws %>% 
  group_by(.draw, gender, country) %>% 
  summarise(country_mean = mean(.prediction), country_cv = 100 * sd(.prediction) / country_mean)


country_lic_players_pred %>% 
  summarise(gender_mean = mean(country_mean), gender_cv = mean(country_cv)) %>% 
  pivot_wider(names_from = gender, values_from = c(gender_mean, gender_cv)) %>% 
  mutate(mean_diff = gender_mean_Men - gender_mean_Women, cv_diff = gender_cv_Men - gender_cv_Women) %>% 
  ungroup() %>% 
  mean_hdi(mean_diff, cv_diff)
```

Countries above or below average:

```{r}
country_lic_players_prob_sup <- country_lic_players_pred %>% 
  mutate(gender_mean = mean(country_mean), gender_cv = mean(country_cv)) %>% 
  group_by(gender, country) %>% 
  summarise(
    prob_sup_m = mean(country_mean > gender_mean), 
    prob_sup_cv = mean(country_cv > gender_cv)
  ) %>% 
    mutate(
    group_m = dplyr::case_when(
        prob_sup_m > .95 ~ "Above",
        prob_sup_m < (1 - .95) ~ "Below",
        TRUE ~ "Average"
      ),
    group_cv = dplyr::case_when(
        prob_sup_cv > .95 ~ "Above",
        prob_sup_cv < (1 - .95) ~ "Below",
        TRUE ~ "Average"
      )
  )

country_lic_players_prob_sup %>% 
  count(group_m)
```

```{r}
country_lic_players_prob_sup %>% 
  filter(group_m != "Average") %>% 
  arrange(gender, group_m, country)
```

Diff in mean:

```{r}
nr_youth_lic_players_draws %>% 
  group_by(gender, country, .draw) %>% 
  summarise(.prediction = mean(.prediction)) %>% 
  group_by(gender, .draw) %>% 
  filter(.prediction == max(.prediction) | .prediction == min(.prediction)) %>% 
  mutate(country = if_else(.prediction == max(.prediction), "max", "min")) %>% 
  pivot_wider(id_cols = c(.draw), names_from = c(gender, country), values_from = .prediction) %>% 
  mutate(men = Men_max - Men_min, women = Women_max - Women_min) %>% 
  ungroup() %>% 
  mean_hdi(men, women)
```

Countries above or below average:

```{r}
country_lic_players_prob_sup %>% 
  count(group_cv)
```

```{r}
country_lic_players_prob_sup %>% 
  filter(group_cv != "Average") %>% 
  arrange(gender, group_cv, country)
```



```{r}
country_prob_sup %>% 
  filter(group_cv %in% c("Above", "Below"))
```

## Selection strategy and ranking

Compare models:

```{r}
loo_compare(loo(nr_youth_ranking_mod), loo(nr_youth_ranking_lic_players_mod))
```


## Selection streategy and senior players

### Country level

Compare models:

```{r}
loo_compare(loo(nr_youth_senior_country_mod), loo(nr_youth_senior_lic_players_country_mod))
```

### Generation level
```{r}
loo_compare(loo(nr_youth_senior_generation_mod), loo(nr_youth_senior_lic_players_generation_mod))
```
