---
title: "Data description"
date: "`r Sys.Date()`"
output:
  github_document:
    html_preview: false
---

```{r setup, include=FALSE}

# Set knitr options
knitr::opts_knit$set(root.dir = here::here())
knitr::opts_chunk$set(echo = FALSE)

# Load packages
library(readr)
library(here)

# Load data
generation_data <- read_csv(here("data", "generation_data.csv"))
country_data <- read_csv(here("data", "country_data.csv"))
senior_championship_players_data <- read_csv(here("data", "senior_championship_players_data.csv"))
data_dictionary_generation_data <- read_csv(here("data", "data_dictionary_generation_data.csv"))
data_dictionary_country_data <- read_csv(here("data", "data_dictionary_country_data.csv"))
data_dictionary_senior_championship_players_data <- read_csv(here("data", "data_dictionary_senior_championship_players_data.csv"))
```

The project includes three datasets:

- `generation_data`
- `country_data`
- `senior_championship_players_data`

## Generation Data

The `generation_data` dataset contains `r nrow(generation_data)` observations (rows) and `r ncol(generation_data)` variable (columns).
Each observation corresponds to one generation of one gender and country.

The `generation_data` contains the following variable:

```{r}
knitr::kable(data_dictionary_generation_data)
```

## Country Data

The `country_data` dataset contains `r nrow(country_data)` observations (rows) and `r ncol(country_data)` variable (columns).
Each observation corresponds to one country and gender.

The `country_data` contains the following variable:

```{r}
knitr::kable(data_dictionary_country_data)
```

## Senior Championship Player Data

The `senior_championship_players_data` dataset contains `r nrow(senior_championship_players_data)` observations (rows) and `r ncol(senior_championship_players_data)` variable (columns).
Each observation corresponds to one player that had played in at least one of the following tournament:

- 2019 Men's FIBA World Cup
- 2017 Men's FIBA Eurobasket
- 2019 Women's FIBA Eurobasket
- 2018 Women's FIBA World Cup
- 2017 Women's FIBA Eurobasket

The `senior_championship_players_data` contains the following variable:

```{r}
knitr::kable(data_dictionary_country_data)
```